\documentclass[11pt]{article}          % use "amsart" instead of "article" for AMSLaTeX format
\pagestyle{empty}
\usepackage[margin=0.5in]{geometry}                           % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}
%\geometry{landscape}                           % Activate for for rotated page geometry
\usepackage[parfill]{parskip}                   % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}                           % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
                                                                % TeX will automatically convert eps --> pdf in pdflatex                
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{clrscode3e}

\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

\begin{document}
%\section{}
%\subsection{}

\textbf{2-4 Inversions}

\textbf{a.} List the five inversions of the array $\langle 2, 3, 8, 6, 1 \rangle$

\textbf{Answer}

$\{ (1,2), (1,3), (1,4), (2,3), (3,4) \}$

\textbf{b.} What array with elements from the set $\{ 1, 2, ..., n \}$ has the most inversions?
How many does it have?

\textbf{Answer}

It is the sorted array from $[1 \twodots n]$ which have all permutations possible in the collection
that give us $(n-1) + (n-2) + (n-3) + ... + 1$ which is the summation of $n-1$ numbers, which
gives us $n(n-1)/2$ inversions.

\textbf{c.} What is the relationship between the running time of insertion sort and the number of
inversions in the input array? Justify your answer.

\textbf{Answer}

The number of inversions can be related to the swaps made on insertion sort. So, given a reversed
sorted array, the number of swaps will be proportional to the number of inversion on sorted array.

\textbf{d.} Give an algorithm that determines the number of inversions in any permutation on $n$
elements in $\Theta (n \lg n)$ worst-case time. (Hint: Modify merge sort.)

\textbf{Answer}

The basic idea is to count every swap made on $MERGE-SORT$. And then we subtract from summation of
$n-1$ with the number of swaps made.

$INVERSIONS(A) = \sum_{i=0}^{n} i - $ number of swaps in $MERGESORT$

\end{document}
